---
title: "Assignment 7"
author: "Michael Gorman"
date: "5/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, eval = FALSE)

library("cowplot")
library("magick")

```

# Question 1

Because the FIPS code in the CSV file was malformed (the leading zero was missing), I lightly processed the data in R before reading it into Mapshaper:

```{r}

read_csv("pop_18_poverty.csv", col_types = cols(Geo_FIPS = col_character(),
                                                Geo_NAME = col_character(),
                                                Geo_QName = col_character(),
                                                pop_18_in_poverty = col_double())) %>%
  mutate(Geo_FIPS = case_when(str_length(Geo_FIPS) == 4 ~ paste0("0", Geo_FIPS),
                              TRUE ~ Geo_FIPS)) %>%
  write_csv("poverty_data.csv")

```

When reading the files into Mapshaper, I used the `string-fields=Geo_FIPS` import option.

Once the data were in Mapshaper, I ran the following commands on the county layer:

```{bash}

proj albersusa
points
join poverty_data keys=GEOID,Geo_FIPS
style r=Math.sqrt(pop_18_in_poverty/300) fill=#f2a83b

```

I then ran the following commands on the state layer:

```{bash}

proj albersusa
style fill=#ecedee stroke=#000

```

The resulting SVG is displayed below and available at https://michaelcgorman.github.io/ppha-30560/assignment-7/mapshaper-output/image.svg

```{r echo = FALSE, eval = TRUE}

# source: https://stackoverflow.com/a/58705542
fig_svg<-cowplot::ggdraw()+cowplot::draw_image("mapshaper-output/image.svg")
plot(fig_svg)

```

# Question 2

The D3 version is available at https://michaelcgorman.github.io/ppha-30560/assignment-7/


